Modelling BCG vaccination in the UK

### 2020-01-07 rmds/02-background.Rmd

## Wordcount: 3668
##packages
##Install via 
##Dev Version:: devtools::install_github("seabbs/tbinenglanddataclean")
library(tbinenglanddataclean)
library(prettypublisher)
library(tidyverse)
library(kableExtra)
library(pander)
library(getTBinR)
##Resources path
resources_path  <- file.path("chapters", "background")
```

>>>>

## Wordcount: 3651
##packages
##Install via 
##Dev Version:: devtools::install_github("seabbs/tbinenglanddataclean")
library(tbinenglanddataclean)
library(prettypublisher)
library(tidyverse)
library(kableExtra)
library(pander)
library(getTBinR)
##Resources path
resources_path  <- file.path("chapters", "background")
```

### 2020-01-07 rmds/03-getTBinR.Rmd

```{r gettbinr-setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 320, cache = TRUE,
                      fig.width = 8, fig.height = 8,
                      out.width = "80%", fig.align = 'center')
## Wordcount:2124
##packages
## Install via 
## CRAN: install.packages("getTBinR")
## Dev Version:: devtools::install_github("seabbs/getTBinR", update = TRUE)
library(getTBinR)
library(tidyverse)
## Resources path
resources_path <- file.path("chapters", "getTBinR")
```

>>>>

```{r gettbinr-setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 320, cache = TRUE,
                      fig.width = 8, fig.height = 8,
                      out.width = "80%", fig.align = 'center')
## Wordcount:2114
##packages
## Install via 
## CRAN: install.packages("getTBinR")
## Dev Version:: devtools::install_github("seabbs/getTBinR", update = TRUE)
library(getTBinR)
library(tidyverse)
## Resources path
resources_path <- file.path("chapters", "getTBinR")
```

### 2020-01-07 rmds/index.Rmd

---
author: 'Samuel Abbott'
date: 'August 2019'
division: 'Bristol Medical School\: Population Health Sciences'
advisor: 'Ellen Brooks Pollock'
altadvisor: 'Hannah Christensen'
department: 'Faculty of Health Sciences'
title: 'Modelling BCG vaccination in the UK'
subtitle: 'What is the impact of changing policy?'
wordcount: "55,287"
knit: "bookdown::render_book"
site: "bookdown::bookdown_site"
always_allow_html: yes
output: 
  ##Thesis can only be fully built for pdf using the makefile
  thesisdown::thesis_pdf: default
  #thesisdown::thesis_gitbook: default
  #thesisdown::thesis_word: default
  #thesisdown::thesis_epub: default
bibliography: ["bib/thesis.bib"]
#Download your specific bibliography database file and refer to it in the line above.
link-citations: yes
colorlinks: yes
csl: ["csl/bmj.csl"]
#Download your specific csl file and refer to it in the line above.
lot: true
lof: true
space_between_paragraphs: true
#Delete the # at the beginning of the previous line if you'd like
#to have a blank new line between each paragraph
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}

>>>>

---
author: 'Samuel Abbott'
date: 'August 2019'
division: 'Bristol Medical School\: Population Health Sciences'
advisor: 'Ellen Brooks Pollock'
altadvisor: 'Hannah Christensen'
department: 'Faculty of Health Sciences'
title: 'Modelling BCG vaccination in the UK'
subtitle: 'What is the impact of changing policy?'
wordcount: "57,481"
knit: "bookdown::render_book"
site: "bookdown::bookdown_site"
always_allow_html: yes
output: 
  ##Thesis can only be fully built for pdf using the makefile
  thesisdown::thesis_pdf: default
  #thesisdown::thesis_gitbook: default
  #thesisdown::thesis_word: default
  #thesisdown::thesis_epub: default
bibliography: ["bib/thesis.bib"]
#Download your specific bibliography database file and refer to it in the line above.
link-citations: yes
colorlinks: yes
csl: ["csl/bmj.csl"]
#Download your specific csl file and refer to it in the line above.
lot: true
lof: true
space_between_paragraphs: true
#Delete the # at the beginning of the previous line if you'd like
#to have a blank new line between each paragraph
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
